---
title: "Supplementary Material"
author: "Gerry Tonkin-Hill"
date: "`r Sys.Date()`"
output: 
  html_document:
    fig_width: 12
    fig_height: 8
editor_options: 
  chunk_output_type: console
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=20, fig.height=12,
                      echo=TRUE, warning=FALSE, message=FALSE,
                      tidy=TRUE)
options(stringsAsFactors = FALSE)
```

## Libraries

```{r}
library(fastbaps)
library(rhierbaps)
library(ggtree)
library(phytools)
library(ggtree)
library(ggplot2)
library(data.table)
library(patchwork)
library(stringr)
library(dplyr)
library(Matrix)
library(ggbeeswarm)

set.seed(1234)
```

```{r}
plot_custom_ggtree <- function(tree, multi.baps, multi.hc, multi.flat, hb, bbp){
  colnames(multi.baps)[2:ncol(multi.baps)] <- paste("baps", colnames(multi.baps)[2:ncol(multi.baps)], sep="_")
  colnames(multi.hc)[2:ncol(multi.hc)] <- paste("hc", colnames(multi.hc)[2:ncol(multi.hc)], sep="_")
  colnames(multi.flat)[2:ncol(multi.flat)] <- paste("flat", colnames(multi.flat)[2:ncol(multi.flat)], sep="_")
  
  multi <- merge(multi.baps, multi.hc, by.x = "Isolates", by.y="Isolates")
  multi <- merge(multi, multi.flat, by.x = "Isolates", by.y="Isolates")
  
  multi$bbp.tree <- bbp[match(multi$Isolates, names(bbp))]
  multi$HB1 <- hb$`level 1`[match(multi$Isolates, hb$Isolate)]
  multi$HB2 <- hb$`level 2`[match(multi$Isolates, hb$Isolate)]

  
  gg <- ggtree(tree)
  f1 <- facet_plot(gg, panel="hierBAPS L1", data=multi, geom=geom_tile, aes(x=HB1), fill='#e41a1c')
  f1 <- facet_plot(f1, panel="hierBAPS L2", data=multi, geom=geom_tile, aes(x=HB2), fill='#377eb8')
  f1 <- facet_plot(f1, panel="Level 1 - BAPS prior", data=multi, geom=geom_tile, aes(x=`baps_Level 1`), fill='#4daf4a')
  f1 <- facet_plot(f1, panel="Level 2 - BAPS prior", data=multi, geom=geom_tile, aes(x=`baps_Level 2`), fill='#984ea3')
  f1 <- facet_plot(f1, panel="Level 1 - HC prior", data=multi, geom=geom_tile, aes(x=`hc_Level 1`), fill='#ff7f00')
  f1 <- facet_plot(f1, panel="Level 2 - HC prior", data=multi, geom=geom_tile, aes(x=`hc_Level 2`), fill='#f781bf')
  f1 <- facet_plot(f1, panel="Level 1 - flat prior", data=multi, geom=geom_tile, aes(x=`flat_Level 1`), fill='#b2df8a')
  f1 <- facet_plot(f1, panel="Level 2 - flat prior", data=multi, geom=geom_tile, aes(x=`flat_Level 2`), fill='#cab2d6')
  f1 <- facet_plot(f1, panel="bbp.tree", data=multi, geom=geom_tile, aes(x=bbp.tree), fill='#a65628')
  f1 <- f1 + theme(text = element_text(size=15))
  return(f1)
}

plot_custom_ggtree_snap <- function(tree, multi.baps, multi.hc, multi.flat, hb, bbp, snap){
  colnames(multi.baps)[2:ncol(multi.baps)] <- paste("baps", colnames(multi.baps)[2:ncol(multi.baps)], sep="_")
  colnames(multi.hc)[2:ncol(multi.hc)] <- paste("hc", colnames(multi.hc)[2:ncol(multi.hc)], sep="_")
  colnames(multi.flat)[2:ncol(multi.flat)] <- paste("flat", colnames(multi.flat)[2:ncol(multi.flat)], sep="_")
  
  multi <- merge(multi.baps, multi.hc, by.x = "Isolates", by.y="Isolates")
  multi <- merge(multi, multi.flat, by.x = "Isolates", by.y="Isolates")
  
  multi$bbp.tree <- bbp[match(multi$Isolates, names(bbp))]
  multi$HB1 <- hb$`level 1`[match(multi$Isolates, hb$Isolate)]
  multi$HB2 <- hb$`level 2`[match(multi$Isolates, hb$Isolate)]
  multi$snap <- snap[match(multi$Isolates, names(snap))]

  
  gg <- ggtree(tree) + geom_text2(aes(subset=!isTip, label=label), hjust=-.1)
  f1 <- facet_plot(gg, panel="hierBAPS L1", data=multi, geom=geom_tile, aes(x=HB1), fill='#e41a1c')
  f1 <- facet_plot(f1, panel="hierBAPS L2", data=multi, geom=geom_tile, aes(x=HB2), fill='#377eb8')
  f1 <- facet_plot(f1, panel="Level 1 - BAPS prior", data=multi, geom=geom_tile, aes(x=`baps_Level 1`), fill='#4daf4a')
  f1 <- facet_plot(f1, panel="Level 2 - BAPS prior", data=multi, geom=geom_tile, aes(x=`baps_Level 2`), fill='#984ea3')
  f1 <- facet_plot(f1, panel="Level 1 - HC prior", data=multi, geom=geom_tile, aes(x=`hc_Level 1`), fill='#ff7f00')
  f1 <- facet_plot(f1, panel="snapclust AIC", data=multi, geom=geom_tile, aes(x=snap), fill='#f781bf')
  f1 <- facet_plot(f1, panel="Level 1 - flat prior", data=multi, geom=geom_tile, aes(x=`flat_Level 1`), fill='#b2df8a')
  f1 <- facet_plot(f1, panel="Level 2 - flat prior", data=multi, geom=geom_tile, aes(x=`flat_Level 2`), fill='#cab2d6')
  f1 <- facet_plot(f1, panel="bbp.tree", data=multi, geom=geom_tile, aes(x=bbp.tree), fill='#a65628')
  f1 <- f1 + theme(text = element_text(size=15))
  return(f1)
}


plot_custom_ggtree_snap_2 <- function(tree, multi.baps, multi.hc, multi.flat, hb, bbp, snap){
  colnames(multi.baps)[2:ncol(multi.baps)] <- paste("baps", colnames(multi.baps)[2:ncol(multi.baps)], sep="_")
  colnames(multi.hc)[2:ncol(multi.hc)] <- paste("hc", colnames(multi.hc)[2:ncol(multi.hc)], sep="_")
  colnames(multi.flat)[2:ncol(multi.flat)] <- paste("flat", colnames(multi.flat)[2:ncol(multi.flat)], sep="_")
  
  multi <- merge(multi.baps, multi.hc, by.x = "Isolates", by.y="Isolates")
  multi <- merge(multi, multi.flat, by.x = "Isolates", by.y="Isolates")
  
  multi$bbp.tree <- bbp[match(multi$Isolates, names(bbp))]
  multi$HB1 <- hb$`level 1`[match(multi$Isolates, hb$Isolate)]
  multi$HB2 <- hb$`level 2`[match(multi$Isolates, hb$Isolate)]
  multi$snap <- snap[match(multi$Isolates, names(snap))]

  
  gg <- ggtree(tree) + geom_text2(aes(subset=!isTip, label=label), hjust=-.1)
  f1 <- facet_plot(gg, panel="hierBAPS", data=multi, geom=geom_tile, aes(x=HB1), fill='#e41a1c')
    f1 <- facet_plot(f1, panel="snapclust AIC", data=multi, geom=geom_tile, aes(x=snap), fill='#f781bf')
  f1 <- facet_plot(f1, panel="BHC prior", data=multi, geom=geom_tile, aes(x=`hc_Level 1`), fill='#ff7f00')
  f1 <- facet_plot(f1, panel="optimised BAPs prior", data=multi, geom=geom_tile, aes(x=`flat_Level 1`), fill='#b2df8a')
  f1 <- facet_plot(f1, panel="best BAPs partition fasttree", data=multi, geom=geom_tile, aes(x=bbp.tree), fill='#a65628')
  f1 <- f1 + theme(text = element_text(size=15))
  return(f1)
}

plot_custom_ggtree_snap_3 <- function(tree, multi.baps, multi.hc, multi.flat, hb, bbp, snap){
  colnames(multi.baps)[2:ncol(multi.baps)] <- paste("baps", colnames(multi.baps)[2:ncol(multi.baps)], sep="_")
  colnames(multi.hc)[2:ncol(multi.hc)] <- paste("hc", colnames(multi.hc)[2:ncol(multi.hc)], sep="_")
  colnames(multi.flat)[2:ncol(multi.flat)] <- paste("flat", colnames(multi.flat)[2:ncol(multi.flat)], sep="_")
  
  multi <- merge(multi.baps, multi.hc, by.x = "Isolates", by.y="Isolates")
  multi <- merge(multi, multi.flat, by.x = "Isolates", by.y="Isolates")
  
  multi$bbp.tree <- bbp[match(multi$Isolates, names(bbp))]
  multi$HB1 <- hb$`level 1`[match(multi$Isolates, hb$Isolate)]
  multi$HB2 <- hb$`level 2`[match(multi$Isolates, hb$Isolate)]
  multi$snap <- snap[match(multi$Isolates, names(snap))]

  
  gg <- ggtree(tree) + geom_text2(aes(subset=!isTip, label=label), hjust=-.1)
  f1 <- facet_plot(gg, panel="hierBAPS", data=multi, geom=geom_tile, aes(x=HB1), fill='#e41a1c')
  f1 <- facet_plot(f1, panel="snapclust AIC", data=multi, geom=geom_tile, aes(x=snap), fill='#f781bf')
  f1 <- facet_plot(f1, panel="BHC prior", data=multi, geom=geom_tile, aes(x=`hc_Level 1`), fill='#ff7f00')
  f1 <- facet_plot(f1, panel="optimised symmetric prior", data=multi, geom=geom_tile, aes(x=`flat_Level 1`), fill='#b2df8a')
  f1 <- facet_plot(f1, panel="best BAPs partition fasttree", data=multi, geom=geom_tile, aes(x=bbp.tree), fill='#a65628')
  f1 <- f1 + theme(text = element_text(size=15))
  return(f1)
}
```

##Escherichia Coli

```{r, cache=TRUE}
e.coli.data <- import_fasta_sparse_nt("./data/escherichia_coli/escherichia_coli_core_gene_alignment.snps.aln", prior = "baps")

dim(e.coli.data$snp.matrix)

e.coli.multi.baps <- multi_res_baps(e.coli.data, levels = 2, n.cores = 4)

e.coli.data <- optimise_prior(e.coli.data, type = "hc", n.cores = 4)
e.coli.multi.hc <- multi_res_baps(e.coli.data, levels = 2, n.cores = 4)

e.coli.data <- optimise_prior(e.coli.data, type = "optimise.baps", n.cores = 4)
e.coli.multi.flat <- multi_res_baps(e.coli.data, levels = 2, n.cores = 4)

e.coli.hb <- fread("./data/escherichia_coli/hierbaps_partition.csv", data.table = FALSE)
e.coli.hb <- e.coli.hb[match(e.coli.multi.baps$Isolates, e.coli.hb$Isolate),]

e.coli.snap <- fread("./data/escherichia_coli_core_gene_alignment.snps_snapclust_results.csv", 
                    data.table = FALSE)
e.coli.sum <- fread("./data/escherichia_coli_core_gene_alignment.snps_snapclust_run_summary.csv", 
                    data.table = FALSE)
e.coli.snap.aic <- e.coli.snap[,e.coli.sum$K[which.min(e.coli.sum$AIC)]]
names(e.coli.snap.aic) <- e.coli.snap$Isolate

e.coli.tree <- phytools::read.newick("./data/escherichia_coli/escherichia_coli_core_gene_alignment.snps.aln.fasttree")
# e.coli.tree <- phytools::read.newick("./data/iqtree/escherichia_coli_core_gene_alignment.snps.aln.treefile")
temp.label <- str_split_fixed(e.coli.tree$tip.label, pattern = "_", n=2)
e.coli.tree$tip.label <- paste(temp.label[,1], gsub("_", "#", temp.label[,2]), sep="_")

e.coli.tree <- phytools::midpoint.root(e.coli.tree)
e.coli.bbp.tree <- fastbaps::best_baps_partition(e.coli.data, e.coli.tree)

plot_custom_ggtree_snap(tree = e.coli.tree, multi.baps = e.coli.multi.baps,
                   multi.hc = e.coli.multi.hc,
                   multi.flat = e.coli.multi.flat,
                   hb = e.coli.hb, bbp = e.coli.bbp.tree,
                   snap = e.coli.snap.aic)
```

##Haemophilus Influenzae

```{r, cache=TRUE}
h.inf.data <- import_fasta_sparse_nt("./data/haemophilus_influenzae/haemophilus_influenzae_core_gene_snps.aln", prior = "baps")

dim(h.inf.data$snp.matrix)

h.inf.multi.baps <- multi_res_baps(h.inf.data, levels = 2, n.cores = 4)

h.inf.data <- optimise_prior(h.inf.data, type = "hc", n.cores = 4)
h.inf.multi.hc <- multi_res_baps(h.inf.data, levels = 2, n.cores = 4)

h.inf.data <- optimise_prior(h.inf.data, type = "optimise.baps", n.cores = 4)
h.inf.multi.flat <- multi_res_baps(h.inf.data, levels = 2, n.cores = 4)

h.inf.hb <- fread("./data/haemophilus_influenzae_core_gene_snps_hierbaps_partition.csv", data.table = FALSE)
h.inf.hb <- h.inf.hb[match(h.inf.multi.baps$Isolates, h.inf.hb$Isolate),]

h.inf.snap <- fread("./data/haemophilus_influenzae/haemophilus_influenzae_core_gene_snps_snapclust_results.csv", 
                    data.table = FALSE)
h.inf.sum <- fread("./data/haemophilus_influenzae/haemophilus_influenzae_core_gene_snps_snapclust_run_summary.csv", 
                    data.table = FALSE)
h.inf.snap.aic <- h.inf.snap[,h.inf.sum$K[which.min(h.inf.sum$AIC)]]
names(h.inf.snap.aic) <- h.inf.snap$Isolate

h.inf.tree <- phytools::read.newick("./data/haemophilus_influenzae/haemophilus_influenzae_core_gene_snps.aln.fasttree")
# h.inf.tree <- phytools::read.newick("./data/iqtree/haemophilus_influenzae_core_gene_snps.aln.treefile")
temp.label <- str_split_fixed(h.inf.tree$tip.label, pattern = "_", n=2)
h.inf.tree$tip.label <- paste(temp.label[,1], gsub("_", "#", temp.label[,2]), sep="_")

h.inf.tree <- phytools::midpoint.root(h.inf.tree)
h.inf.bbp.tree <- fastbaps::best_baps_partition(h.inf.data, h.inf.tree)

plot_custom_ggtree_snap(tree = h.inf.tree, multi.baps = h.inf.multi.baps,
                   multi.hc = h.inf.multi.hc,
                   multi.flat = h.inf.multi.flat,
                   hb = h.inf.hb, bbp = h.inf.bbp.tree,
                   snap = h.inf.snap.aic)
```


```{r}
plot_custom_ggtree_snap_2(tree = h.inf.tree, multi.baps = h.inf.multi.baps,
                   multi.hc = h.inf.multi.hc,
                   multi.flat = h.inf.multi.flat,
                   hb = h.inf.hb, bbp = h.inf.bbp.tree,
                   snap = h.inf.snap.aic)
```

Can use bootstrap to gain a feeling for the confidence of our results

```{r}
h.inf.boot.m <- boot_fast_baps(h.inf.data)
h.inf.hc <- as.dendrogram(fast_baps(h.inf.data))
gplots::heatmap.2(h.inf.boot.m, h.inf.hc, h.inf.hc, labRow = FALSE, labCol = FALSE,tracecol=NA)
```

##Listeria Monocytogenes

```{r, cache=TRUE}
listeria.data <- fastbaps::import_fasta_sparse_nt("./data/listeria_monocytogenes/listeria_monocytogenes_core_gene_snps.aln", prior = "baps")
dim(listeria.data$snp.matrix)

listeria.multi.baps <- multi_res_baps(listeria.data, levels = 2, n.cores = 4)

listeria.data <- optimise_prior(listeria.data, type = "hc", n.cores = 4)
listeria.multi.hc <- multi_res_baps(listeria.data, levels = 2, n.cores = 4)

listeria.data <- optimise_prior(listeria.data, type = "optimise.baps", n.cores = 4)
listeria.multi.flat <- multi_res_baps(listeria.data, levels = 2, n.cores = 4)

listeria.hb <- fread("./data/listeria_monocytogenes_core_gene_snps_hierbaps_partition.csv", data.table = FALSE)
listeria.hb <- listeria.hb[match(listeria.multi.hc$Isolates, listeria.hb$Isolate),]

listeria.snap <- fread("./data/listeria_monocytogenes_core_gene_snps_snapclust_results.csv", 
                    data.table = FALSE)
listeria.sum <- fread("./data/listeria_monocytogenes_core_gene_snps_snapclust_run_summary.csv", 
                    data.table = FALSE)
listeria.snap.aic <- listeria.snap[,listeria.sum$K[which.min(listeria.sum$AIC)]]
names(listeria.snap.aic) <- listeria.snap$Isolate

listeria.tree <- ape::read.tree("./data/listeria_monocytogenes/listeria_monocytogenes_core_gene_snps.aln.fasttree")
# listeria.tree <- phytools::read.newick("./data/iqtree/listeria_monocytogenes_core_gene_snps.aln.treefile")
temp.label <- str_split_fixed(listeria.tree$tip.label, pattern = "_", n=2)
listeria.tree$tip.label <- paste(temp.label[,1], gsub("_", "#", temp.label[,2]), sep="_")

listeria.tree <- phytools::midpoint.root(listeria.tree)
listeria.bbp.tree <- fastbaps::best_baps_partition(listeria.data, listeria.tree)

gg <- ggtree(listeria.tree) + geom_text2(aes(subset=!isTip, label=label), hjust=-.1)
f1 <- facet_plot(gg, panel="listeria.multi.flat", data=listeria.multi.flat, geom=geom_tile, aes(x=`Level 1`), fill='#e41a1c')
f1

plot_custom_ggtree_snap(tree = listeria.tree, multi.baps = listeria.multi.baps,
                   multi.hc = listeria.multi.hc,
                   multi.flat = listeria.multi.flat,
                   hb = listeria.hb, bbp = listeria.bbp.tree,
                   snap = listeria.snap.aic)
```

##Neisseria Meningitidis

```{r, cache=TRUE}
n.meng.data <- import_fasta_sparse_nt("./data/neisseria_meningitidis/neisseria_meningitidis_core_gene_snps.aln", prior = "baps")
dim(n.meng.data$snp.matrix)

n.meng.multi.baps <- multi_res_baps(n.meng.data, levels = 2, n.cores = 4)

n.meng.data <- optimise_prior(n.meng.data, type = "hc", n.cores = 4)
n.meng.multi.hc <- multi_res_baps(n.meng.data, levels = 2, n.cores = 4)

n.meng.data <- optimise_prior(n.meng.data, type = "optimise.baps", n.cores = 4)
n.meng.multi.flat <- multi_res_baps(n.meng.data, levels = 2, n.cores = 4)


n.meng.hb <- fread("./data/neisseria_meningitidis_core_gene_snps_hierbaps_partition.csv", data.table = FALSE)
n.meng.hb <- n.meng.hb[match(n.meng.multi.baps$Isolates, n.meng.hb$Isolate),]

n.meng.snap <- fread("./data/neisseria_meningitidis_core_gene_snps_snapclust_results.csv", 
                    data.table = FALSE)
n.meng.sum <- fread("./data/neisseria_meningitidis_core_gene_snps_snapclust_run_summary.csv", 
                    data.table = FALSE)
n.meng.snap.aic <- n.meng.snap[,n.meng.sum$K[which.min(n.meng.sum$AIC)]]
names(n.meng.snap.aic) <- n.meng.snap$Isolate

n.meng.tree <- phytools::read.newick("./data/neisseria_meningitidis/neisseria_meningitidis_core_gene_snps.aln.fasttree")
# n.meng.tree <- phytools::read.newick("./data/iqtree/neisseria_meningitidis_core_gene_snps.aln.treefile")
temp.label <- str_split_fixed(n.meng.tree$tip.label, pattern = "_", n=2)
n.meng.tree$tip.label <- paste(temp.label[,1], gsub("_", "#", temp.label[,2]), sep="_")

n.meng.tree <- phytools::midpoint.root(n.meng.tree)
n.meng.bbp.tree <- fastbaps::best_baps_partition(n.meng.data, n.meng.tree)

plot_custom_ggtree_snap(n.meng.tree, multi.baps = n.meng.multi.baps,
                   multi.hc = n.meng.multi.hc,
                   multi.flat = n.meng.multi.flat,
                   hb = n.meng.hb, bbp = n.meng.bbp.tree,
                   snap = n.meng.snap.aic)
```

```{r}
plot_custom_ggtree_snap_2(n.meng.tree, multi.baps = n.meng.multi.baps,
                   multi.hc = n.meng.multi.hc,
                   multi.flat = n.meng.multi.flat,
                   hb = n.meng.hb, bbp = n.meng.bbp.tree,
                   snap = n.meng.snap.aic)
```

##Staphylococcus Aureus 

```{r, cache=TRUE}
s.aus.data <- import_fasta_sparse_nt("./data/staphylococcus_aureus/staphylococcus_aureus_core_gene_alignment.snps.aln", prior = "baps")
dim(s.aus.data$snp.matrix)

s.aus.multi.baps <- multi_res_baps(s.aus.data, levels = 2, n.cores = 4)

s.aus.data <- optimise_prior(s.aus.data, type = "hc", n.cores=4)

s.aus.multi.hc <- multi_res_baps(s.aus.data, levels = 2, n.cores = 4)

s.aus.data <- optimise_prior(s.aus.data, type = "optimise.baps", n.cores = 4)
s.aus.multi.flat <- multi_res_baps(s.aus.data, levels = 2, n.cores = 4)

s.aus.hb <- fread("./data/staphylococcus_aureus_core_gene_alignment.snps_hierbaps_partition.csv", data.table = FALSE)
s.aus.hb <- s.aus.hb[match(s.aus.multi.baps$Isolates, s.aus.hb$Isolate),]

s.aus.tree <- phytools::read.newick("./data/staphylococcus_aureus/staphylococcus_aureus_core_gene_alignment.snps.aln.fasttree")
# s.aus.tree <- phytools::read.newick("./data/iqtree/staphylococcus_aureus_core_gene_alignment.snps.aln.treefile")
temp.label <- str_split_fixed(s.aus.tree$tip.label, pattern = "_", n=2)
s.aus.tree$tip.label <- paste(temp.label[,1], gsub("_", "#", temp.label[,2]), sep="_")

s.aus.snap <- fread("./data/staphylococcus_aureus_core_gene_alignment.snps_snapclust_results.csv", 
                    data.table = FALSE)
s.aus.sum <- fread("./data/staphylococcus_aureus_core_gene_alignment.snps_snapclust_run_summary.csv", 
                    data.table = FALSE)
s.aus.snap.aic <- s.aus.snap[,s.aus.sum$K[which.min(s.aus.sum$AIC)]]
names(s.aus.snap.aic) <- s.aus.snap$Isolate

s.aus.tree <- phytools::midpoint.root(s.aus.tree)
s.aus.bbp.tree <- fastbaps::best_baps_partition(s.aus.data, s.aus.tree)

plot_custom_ggtree_snap(s.aus.tree, multi.baps = s.aus.multi.baps,
                   multi.flat = s.aus.multi.flat,
                   multi.hc = s.aus.multi.hc,
                   hb = s.aus.hb, bbp = s.aus.bbp.tree,
                   snap = s.aus.snap.aic)
```

```{r}
plot_custom_ggtree_snap_2(s.aus.tree, multi.baps = s.aus.multi.baps,
                   multi.flat = s.aus.multi.flat,
                   multi.hc = s.aus.multi.hc,
                   hb = s.aus.hb, bbp = s.aus.bbp.tree,
                   snap = s.aus.snap.aic)
```

##Ebola

```{r, cache=TRUE}
ebola.data <- import_fasta_sparse_nt("./data/ebola/Makona_1610_cds_ig.fas", prior = "baps")
dim(ebola.data$snp.matrix)

ebola.multi.baps <- multi_res_baps(ebola.data, levels = 2, n.cores = 4)

ebola.data <- optimise_prior(ebola.data, type = "hc", n.cores = 4)
ebola.multi.hc <- multi_res_baps(ebola.data, levels = 2, n.cores = 4)

# ebola.data <- optimise_prior(ebola.data, type = "optimise.baps", n.cores = 4)
# d <- snp_dist(ebola.data)
# h <- hclust(as.dist(d), method="ward.D2")
# ebola.multi.hc <- multi_level_best_baps_partition(ebola.data, h, levels = 2, n.cores = 4)

ebola.data <- optimise_prior(ebola.data, type = "symmetric", n.cores = 4)

ebola.multi.flat <- multi_res_baps(ebola.data, levels = 2, n.cores = 4)

ebola.hb <- fread("./data/Makona_1610_cds_ig_hierbaps_partition.csv", data.table = FALSE)
ebola.hb <- ebola.hb[match(ebola.multi.baps$Isolates, ebola.hb$Isolate),]

ebola.snap <- fread("./data/Makona_1610_cds_ig_snapclust_results.csv", 
                    data.table = FALSE)
ebola.sum <- fread("./data/Makona_1610_cds_ig_snapclust_run_summary.csv", 
                    data.table = FALSE)
ebola.snap.aic <- ebola.snap[,ebola.sum$K[which.min(ebola.sum$AIC)]]
names(ebola.snap.aic) <- ebola.snap$Isolate


# ebola.tree <- phytools::read.newick("./data/ebola/Makona_1610_cds_ig_iqtree_allnni.treefile")
ebola.tree <- phytools::read.newick("./data/iqtree/Makona_1610_cds_ig.fas.treefile")

plot(ebola.tree, show.tip.label = FALSE)
ebola.tree <- phytools::midpoint.root(ebola.tree)
ebola.bbp.tree <- fastbaps::best_baps_partition(ebola.data, ebola.tree)

plot_custom_ggtree_snap(tree = ebola.tree, hb = ebola.hb,
                   multi.baps = ebola.multi.baps,
                   multi.hc = ebola.multi.hc,
                   multi.flat = ebola.multi.flat,
                   bbp = ebola.bbp.tree,
                   snap = ebola.snap.aic)
```

```{r}
plot_custom_ggtree_snap_3(tree = ebola.tree, hb = ebola.hb,
                   multi.baps = ebola.multi.baps,
                   multi.hc = ebola.multi.hc,
                   multi.flat = ebola.multi.flat,
                   bbp = ebola.bbp.tree,
                   snap = ebola.snap.aic)
```

##HIV

Load HIV data and remove outliers

```{r}
hiv.data <- import_fasta_sparse_nt("./data/HIV/hiv_refs_prrt_trim.fas", prior = "baps")

cs <- colSums(hiv.data$snp.matrix>0)
hist(cs, breaks=100)
sum(cs>200)

hiv.data$snp.matrix <- hiv.data$snp.matrix[,cs<200]
```

```{r, eval=FALSE}
system.time({hiv.data <- optimise_prior(hiv.data, type = "symmetric", n.cores = 10)})

system.time({hiv.multi <- multi_res_baps(hiv.data, levels = 1, n.cores = 10, k.init = 11000)})

write.csv(hiv.multi, file="./processed_data/hiv_multi_opt_baps_prior_l1.csv", quote=FALSE)
```

```{r, eval=FALSE}
system.time({hiv.data <- optimise_prior(hiv.data, type = "optimise.baps", n.cores = 10)})

system.time({hiv.multi <- multi_res_baps(hiv.data, levels = 1, n.cores = 10, k.init = 11000)})

write.csv(hiv.multi, file="./processed_data/hiv_multi_opt_symmetric_prior_l1.csv", quote=FALSE)
```

```{r}
hiv.multi.opt.baps <- fread("./processed_data/hiv_multi_opt_baps_prior_l1.csv", data.table = FALSE)

hiv.multi.opt.symmetric <- fread("./processed_data/hiv_multi_opt_symmetric_prior_l1.csv", data.table = FALSE)
```

Choose a pretty silly outgroup as the earliest sample.

```{r}
hiv.tree <- phytools::read.newick("./data/HIV/hiv_refs_prrt_trim.fas.fasttree")
bad.tips <- hiv.tree$tip.label[!(hiv.tree$tip.label %in% hiv.multi.opt.baps$Isolates)]
hiv.tree <- ape::drop.tip(hiv.tree, tip = bad.tips)

longest.edge <- hiv.tree$edge[order(-hiv.tree$edge.length)][1:100]
long.nodes <- hiv.tree$edge[longest.edge,]     #this should usually include one tip
new.outgroup <- long.nodes[long.nodes < Ntip(hiv.tree)][[1]]
tree.rooted <- root(hiv.tree, outgroup=new.outgroup, resolve.root=T)
```

```{r, eval=FALSE}
hiv.data <- optimise_prior(hiv.data, type="optimise.baps")
best.baps.partition <- fastbaps::best_baps_partition(hiv.data, tree.rooted)

write.table(data.frame(Isolates=names(best.baps.partition), best.baps.partition=best.baps.partition, stringsAsFactors = FALSE),
            file = "./processed_data/best_nbaps_partition_fasttree.csv", sep=",", col.names = TRUE, row.names = FALSE, quote = FALSE)
```

```{r}
best.baps.partition <- fread("./processed_data/best_nbaps_partition_fasttree.csv", data.table = FALSE)

hiv.multi.opt.symmetric <- hiv.multi.opt.symmetric[match(tree.rooted$tip.label, hiv.multi.opt.symmetric$Isolates), ]

hiv.multi.opt.symmetric$V1 <- NULL
hiv.multi.opt.baps$V1 <- NULL

hiv.multi.merged <- merge(hiv.multi.opt.symmetric, hiv.multi.opt.baps, by.x="Isolates", by.y="Isolates")
colnames(hiv.multi.merged) <- c("Isolate", "Level 1.sym", "Level 1.baps")

hiv.multi.merged <- merge(hiv.multi.merged, best.baps.partition, by.x = "Isolate", by.y="Isolates")
```


```{r}
hiv.multi.merged <- hiv.multi.merged[match(tree.rooted$tip.label, hiv.multi.merged$Isolate), ]

par(mfrow=c(1,2))
plot(tree.rooted, show.tip.label=FALSE)
# tiplabels(pch=1,
#     col = hiv.multi.opt.symmetric$`Level 1`)
plot(x = hiv.multi.merged$`Level 1.baps`, 
     y = 1:nrow(hiv.multi.merged), 
     pch=0.1, cex=0.2, axes = FALSE)
par(mfrow=c(1,1))
```

Lets compare to a simple kmeans with a similar number of clusters

first some helper function to find the elbow

```{r}
distance <- function(p, start.point, end.point){
 x1 <- start.point[[1]]
 y1 <- start.point[[2]]
 x2 <- end.point[[1]]
 y2 <- end.point[[2]]
 x0 <- p[[1]]
 y0 <- p[[2]]
 d <- abs((y2-y1)*x0 - (x2-x1)*y0 + x2*y1 - y2*x1)/sqrt((y2-y1)^2 + (x2-x1)^2)
 return(d)
}

elbow <- function(sizes){
 n <- length(sizes)
 x <- 1:n
 start.point <- c(1, sizes[[1]])
 end.point <- c(n, sizes[[n]])
 return(unlist(lapply(1:n, function(i) distance(c(i, sizes[[i]]), start.point, end.point))))
}
```

```{r, eval=FALSE}
set.seed(303)

pc <- irlba::prcomp_irlba(1*t(hiv.data$snp.matrix>0), n=50)

# max(combined.df$best.baps.partition.tree)
all.k <- lapply(1:200, function(k){
  k <- kmeans(pc$x, centers = k, iter.max = 100)
})

#look for the elbow ignoring k=1 as this seems very far from the remaining points
wss <- unlist(lapply(all.k, function(x) x$tot.withinss))
elbow.k <- which.max(elbow(wss[1:length(wss)])) 
plot(wss)
print(elbow.k)
abline(v=elbow.k, col="red")

elbow.k <- all.k[[elbow.k]]$cluster
names(elbow.k) <- colnames(hiv.data$snp.matrix)

hiv.multi.merged$kmeans.21 <- elbow.k[match(hiv.multi.merged$Isolate, names(elbow.k))]

temp.kmeans <- kmeans(pc$x, centers = 193, iter.max = 100)
hiv.multi.merged$kmeans.193 <- temp.kmeans$cluster[match(hiv.multi.merged$Isolate, names(elbow.k))]

#Extract the type and country information from the isolate names

combined.df <- stringr::str_split_fixed(hiv.multi.merged$Isolate, pattern = "\\|", n = 4)
colnames(combined.df) <- c("Isolate", "Type", "Country", "Date")
combined.df <- cbind(combined.df, hiv.multi.merged[,2:ncol(hiv.multi.merged)])

write.table(combined.df, file="./processed_data/combined_clusters.csv", 
            sep=",", quote = FALSE, col.names = TRUE, row.names = FALSE)
```

Look at clustering by type

```{r, fig.height=40, fig.width=12}
combined.df <- fread("./processed_data/combined_clusters.csv", data.table = FALSE)

cluster.types <- lapply(1:max(combined.df$`Level 1.baps`), function(x){
  tb <- table(combined.df$Type[combined.df$`Level 1.baps`==x])
  tb[order(tb)]
})
cluster.types[order(unlist(lapply(cluster.types, sum)))]

cluster.types <- lapply(1:max(combined.df$`Level 1.sym`), function(x){
  tb <- table(combined.df$Country[combined.df$`Level 1.sym`==x])
  tb[order(tb)]
})
cluster.types[order(unlist(lapply(cluster.types, sum)))]
```

Plot propotion of cluster that is it's major type or contains it. I.e type 'AE' would match to both 'A' and 'E'.

```{r}
combined.df <- combined.df[,c("Isolate", "Type", "Country", "Date", "Level 1.sym", "Level 1.baps", "best.baps.partition","kmeans.21", "kmeans.193")]
colnames(combined.df) <- c("Isolate","Type","Country","Date",
                           "Level 1 optimised symmetric prior",
                           "Level 1 optimised BAPs prior",
                           "Best BAPs partition fasttree",
                           "kmeans k=21",
                           "kmeans k=193")


all.method.clust.props <- lapply(5:ncol(combined.df), function(j){
  cluster.types <- lapply(1:max(combined.df[,j]), function(x){
    tb <- table(combined.df$Type[combined.df[,j]==x])
    tb[order(tb)]
  })
  names(cluster.types) <- 1:max(combined.df[,j])
  cluster.types <- cluster.types[order(unlist(lapply(cluster.types, sum)))]
  
  props <- unlist(lapply(cluster.types, function(c.table){
    top <- names(c.table)[which.max(c.table)]
    top.caps <- unlist(strsplit(gsub("[^::A-Z::]","", top), "*"))
    matching <- grepl(paste(top.caps, collapse = "|"), names(c.table))
    return(sum(c.table[matching])/sum(c.table))
  }))
  clust.sizes <- unlist(lapply(cluster.types, sum))
  
  cluster.stats <- data.frame(method = rep(colnames(combined.df)[j], length(props)),
                              cluster = names(props),
                              prop.match.top = props,
                              `cluster size` = clust.sizes, 
                              stringsAsFactors = FALSE)
})
all.method.clust.props <- do.call(rbind, all.method.clust.props)
all.method.clust.props <- all.method.clust.props[!(all.method.clust.props$method %in% c("kmeans k=21")),]

ggplot(all.method.clust.props, aes(x=1, y=prop.match.top)) + geom_violin(aes(fill=method)) +
  geom_beeswarm(aes(size=cluster.size)) +
  facet_wrap(~method, ncol = 2) +
  theme_bw() + ylab("Proportion comprising the dominant HIV subtype") +
  labs(size='cluster size') +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  theme(text = element_text(size=20))
```

Investigate dominant country proportions

```{r}
all.method.clust.props <- lapply(5:ncol(combined.df), function(j){
  cluster.types <- lapply(1:max(combined.df[,j]), function(x){
    tb <- table(combined.df$Country[combined.df[,j]==x])
    tb[order(tb)]
  })
  names(cluster.types) <- 1:max(combined.df[,j])
  cluster.types <- cluster.types[order(unlist(lapply(cluster.types, sum)))]
  
  props <- unlist(lapply(cluster.types, function(c.table){
    top <- names(c.table)[which.max(c.table)]
    matching <- top==names(c.table)
    return(sum(c.table[matching])/sum(c.table))
  }))
  clust.sizes <- unlist(lapply(cluster.types, sum))
  
  cluster.stats <- data.frame(method = rep(colnames(combined.df)[j], length(props)),
                              cluster = names(props),
                              prop.match.top = props,
                              `cluster size` = clust.sizes, 
                              stringsAsFactors = FALSE)
})
all.method.clust.props <- do.call(rbind, all.method.clust.props)
all.method.clust.props <- all.method.clust.props[!(all.method.clust.props$method %in% c("kmeans k=21")),]

ggplot(all.method.clust.props, aes(x=1, y=prop.match.top)) + geom_violin(aes(fill=method)) +
  geom_beeswarm(aes(size=cluster.size)) +
  facet_wrap(~method, ncol = 2) +
  theme_bw() + ylab("Proportion comprising the dominant country") +
  labs(size='cluster size') +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  theme(text = element_text(size=20))
```

umap plot

```{r}
library(umap)
library(Matrix)

hiv.um <- umap::umap(pc$x, method="umap-learn")

combined.df <- combined.df[match(colnames(hiv.data$snp.matrix),
                                 unlist(apply(combined.df[,c(1,2,3,4)], 1, paste, collapse = "|"))),]
combined.df$k.means.21 <- elbow.k

plot.df <- data.frame(Isolates = colnames(hiv.data$snp.matrix), hiv.um$layout, 
                      k.means.193=combined.df$`kmeans k=193`,
                      k.means.21=combined.df$`kmeans k=21`,
                      stringsAsFactors = FALSE)
plot.df <- merge(plot.df, hiv.multi.opt.baps, by.x="Isolates", by.y="Isolates")


palette(c("#ff7f00","#cab2d6","#6a3d9a","#fdbf6f","#ffff99","#1f78b4","#b15928","#33a02c","#e31a1c","#a6cee3","#fb9a99","#b2df8a"))
plot(X2~X1, data=plot.df, col=plot.df$`Level 1`, cex=0.1,
     xlab="", ylab="", 
     cex.axis=1.5, font=1.5)
mtext(side=1, line=3, "UMAP DIM 1", cex=1.5)
mtext(side=2, line=3, "UMAP DIM 2", cex=1.5)

plot(X2~X1, data=plot.df, col=k.means.193, cex=0.1,
     xlab="", ylab="", 
     cex.axis=1.5, font=1.5)
mtext(side=1, line=3, "UMAP DIM 1", cex=1.5)
mtext(side=2, line=3, "UMAP DIM 2", cex=1.5)

plot(X2~X1, data=plot.df, col=k.means.21, cex=0.1,
     xlab="", ylab="", 
     cex.axis=1.5, font=1.5)
mtext(side=1, line=3, "UMAP DIM 1", cex=1.5)
mtext(side=2, line=3, "UMAP DIM 2", cex=1.5)

plot(X2~X1, data=plot.df, col="white", cex=0.1,
     xlab="", ylab="", 
     cex.axis=1.5, font=1.5)
mtext(side=1, line=3, "UMAP DIM 1", cex=1.5)
mtext(side=2, line=3, "UMAP DIM 2", cex=1.5)
text(x =plot.df$X1, y=plot.df$X2, labels = plot.df$`Level 1`, col=plot.df$`Level 1`, cex=0.3)

plot(X2~X1, data=plot.df, col="white", cex=0.1,
     xlab="", ylab="", 
     cex.axis=1.5, font=1.5)
mtext(side=1, line=3, "UMAP DIM 1", cex=1.5)
mtext(side=2, line=3, "UMAP DIM 2", cex=1.5)
text(x =plot.df$X1, y=plot.df$X2, labels = plot.df$k.means.193, col=plot.df$k.means.193, cex=0.3)

plot(X2~X1, data=plot.df, col="white", cex=0.1,
     xlab="", ylab="", 
     cex.axis=1.5, font=1.5)
mtext(side=1, line=3, "UMAP DIM 1", cex=1.5)
mtext(side=2, line=3, "UMAP DIM 2", cex=1.5)
text(x =plot.df$X1, y=plot.df$X2, labels = plot.df$k.means.21, col=plot.df$k.means.21, cex=0.3)

col <- c("#a6cee3","#1f78b4","#b2df8a","#33a02c","#fb9a99","#e31a1c","#fdbf6f","#ff7f00","#cab2d6","#6a3d9a","#b15928")
plot.df$Country <- factor(str_split_fixed(plot.df$Isolates,"\\|", n=4)[,3])
plot(X2~X1, data=plot.df, col="white", cex=0.1,
     xlab="", ylab="", 
     cex.axis=1.5, font=1.5)
mtext(side=1, line=3, "UMAP DIM 1", cex=1.5)
mtext(side=2, line=3, "UMAP DIM 2", cex=1.5)
max.col <- length(unique(plot.df$Country))/length(col)
text(x =plot.df$X1, y=plot.df$X2, labels = plot.df$`Level 1`, col=col[as.numeric(plot.df$Country)/max.col], cex=0.3)

```

Plot clusters on world map

```{r}
summarised.df <- combined.df
summarised.df$Country <- as.character(summarised.df$Country)
summarised.df$temp.interaction <- paste(summarised.df$Country, summarised.df$`Level 1 optimised BAPs prior`)
summarised.df <- summarised.df %>% group_by(temp.interaction) %>%
  summarise(
    Country=unique(Country),
    Cluster=unique(`Level 1 optimised BAPs prior`),
    count=n()
  )
head(summarised.df)

cluster.sizes <- summarised.df %>% group_by(Cluster) %>% summarise(
  count=sum(count)
)

summarised.df$count <- summarised.df$count/cluster.sizes$count[match(summarised.df$Cluster, cluster.sizes$Cluster)]

capitals <- fread("data/capital_locations.tsv", data.table = FALSE)
capitals$Country <- str_to_upper(capitals$Country)
capitals$Country <- gsub(" ", "", capitals$Country)

capitals <- rbind(capitals, data.frame(Country=c(
  "JAPAN", "GRENADA","MONGOLIA","SAINTVINCENTANDTHEGRENADINES","SOUTHKOREA",
  "TRINIDADANDTOBAGO","YEMEN","DEMREPOFCONGO","HONGKONG","MACAU","MONTENEGRO",
  "SERBIA","TAIWAN","UNITEDKINGDOM","DOMINICANREPUBLIC","IRAN","MOLDOVA","RWANDA",
  "SINGAPORE","TANZANIA","UNITEDSTATES",""),
  Capital=c("Tokyo","St. George's","Ulaanbaatar","Kingstown","Seoul","Port of Spain",
            "Sana'a, Aden","Kinshasa","HONGKONG","MACAU","Podgorica","Belgrade","Taipei",
            "London","Santo Domingo","Tehran","Chisinau","Kigali","SINGAPORE","Dodoma",
            "Washington, D.C.",""),
  Latitude=c("35.6895N","12.0561N","47.8864N","13.1600N","37.5665N","10.6549N","15.3694N",
             "4.4419S","22.3964N","22.1987N","42.4304N","44.7866N","25.0330N","51.5074N",
             "18.4861N","35.6892N","47.0105N","1.9706S","1.3521N","6.1630S","38.9072N","0N"),
  Longitude=c("139.6917E", "61.7488W","106.9057E","61.2248W","126.9780E","61.5019W","44.1910E",
              "15.2663E","114.1095E","113.5439E","19.2594E","20.4489E","121.5654E","0.1278W",
              "69.9312W","51.3890E","28.8638E","30.1044E","103.8198E","35.7516E","77.0369W","0E"), 
  stringsAsFactors = FALSE))

temp <- as.numeric(gsub("[N|S]","", capitals$Latitude))
temp[!grepl(".*N.*", capitals$Latitude)] <- -temp[!grepl(".*N.*", capitals$Latitude)]
capitals$Latitude <- temp

temp <- as.numeric(gsub("[E|W]","", capitals$Longitude))
temp[!grepl(".*E.*", capitals$Longitude)] <- -temp[!grepl(".*E.*", capitals$Longitude)]
capitals$Longitude <- temp

capitals <- capitals[capitals$Country %in% summarised.df$Country,]

d <- geosphere::distm(capitals[,c("Longitude","Latitude")])
colnames(d) <- rownames(d) <- capitals$Country
h <- hclust(as.dist(d), method = "ward.D2")

summarised.df$Country <- factor(summarised.df$Country, levels = h$labels[h$order])

ggplot(summarised.df, aes(Cluster, Country)) + 
  geom_tile(aes(fill = count), colour = "white") +
  scale_fill_gradient(low = "lightblue", high = "darkblue") +
  theme(legend.title = element_text(size = 10),
        legend.text = element_text(size = 12),
        plot.title = element_text(size=16),
        axis.title=element_text(size=14,face="bold"),
        axis.text.y = element_text(size=8)) +
  labs(fill = "Proportion") +
  theme_bw()
```

## Investigate Maela

```{r}
maela.data <- fastbaps::import_fasta_sparse_nt("./data/maela/maela3k_snps.fasta")
maela.data <- optimise_prior(maela.data, type = "optimise.baps")

system.time({maela.optimise.baps.multi <- multi_res_baps(maela.data, levels = 2, n.cores = 4)})

maela.data <- optimise_prior(maela.data, type = "baps")
system.time({maela.baps.multi <- multi_res_baps(maela.data, levels = 2, n.cores = 4)})
```

```{r}
library(umap)
library(Matrix)

pc.maela <- irlba::prcomp_irlba(1*t(maela.data$snp.matrix>0), n=50)
um.maela <- umap::umap(pc.maela$x, method="umap-learn")
n.clusters <- max(maela.optimise.baps.multi$`Level 1`)

k.means.79 <- kmeans(pc.maela$x, centers = 79, iter.max = 50, nstart = 5)$cluster

k.max <- 200 # Maximal number of clusters
kmeans.results <- lapply(1:k.max,  function(k){kmeans(pc.maela$x, k, iter.max = 100)})
wss <- unlist(lapply(kmeans.results, function(x) x$tot.withinss))

plot(1:k.max, wss,
       type="b", pch = 19, frame = FALSE, 
       xlab="Number of clusters K",
       ylab="Total within-clusters sum of squares")
which.max(elbow(wss))

k.means.48 <- kmeans(pc.maela$x, centers = 48, iter.max = 50, nstart = 5)$cluster


plot.df <- data.frame(Isolates = colnames(maela.data$snp.matrix), um.maela$layout, 
                      k.means.79=k.means.79, 
                      k.means.48=k.means.48,
                      stringsAsFactors = FALSE)
plot.df <- merge(plot.df, maela.optimise.baps.multi, by.x="Isolates", by.y="Isolates")


palette(c("#a6cee3","#1f78b4","#b2df8a","#33a02c","#fb9a99","#e31a1c","#fdbf6f","#ff7f00","#cab2d6","#6a3d9a","#b15928"))
plot(X2~X1, data=plot.df, col=plot.df$`Level 1`, cex=1,
     xlab="", ylab="", 
     cex.axis=1.5, font=1.5)
mtext(side=1, line=3, "UMAP DIM 1", cex=1.5)
mtext(side=2, line=3, "UMAP DIM 2", cex=1.5)

cols <- list(c(166,206,227),c(31,120,180),c(178,223,138),c(51,160,44),c(251,154,153),c(227,26,28),c(253,191,111),c(255,127,0),c(202,178,214),c(106,61,154),c(177,89,40))
palette(unlist(lapply(cols, function(col) rgb(col[[1]], col[[2]],col[[3]], alpha=100, maxColorValue=255))))

plot(X2~X1, data=plot.df, col="white", cex=0.1,
     xlab="", ylab="", 
     cex.axis=1.5, font=1.5)
mtext(side=1, line=3, "UMAP DIM 1", cex=1.5)
mtext(side=2, line=3, "UMAP DIM 2", cex=1.5)
text(x =plot.df$X1, y=plot.df$X2, labels = plot.df$`Level 1`, col=plot.df$`Level 1`, cex=0.6)

plot(X2~X1, data=plot.df, col="white", cex=0.1,
     xlab="", ylab="", 
     cex.axis=1.5, font=1.5)
mtext(side=1, line=3, "UMAP DIM 1", cex=1.5)
mtext(side=2, line=3, "UMAP DIM 2", cex=1.5)
text(x =plot.df$X1, y=plot.df$X2, labels = plot.df$k.means.48, col=plot.df$k.means.48, cex=0.6)

plot(X2~X1, data=plot.df, col="white", cex=0.1,
     xlab="", ylab="", 
     cex.axis=1.5, font=1.5)
mtext(side=1, line=3, "UMAP DIM 1", cex=1.5)
mtext(side=2, line=3, "UMAP DIM 2", cex=1.5)
text(x =plot.df$X1, y=plot.df$X2, labels = plot.df$k.means.79, col=plot.df$k.means.79, cex=0.6)

```

